\TheTitle

### 2017-07-05 paper/lineval.tex
Results section

>>>>

We recorded the audio and screen capture video for each participant in
the study for further analysis. After capturing the information, we
extracted various metrics from the videos. From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy. Correctness is a binary
value, it is true if the response was correct and false if the response
was incorrect. The accuracy is measures in distance from the correct
value. An accuracy of zero indicates a correct answer. All tasks in the
summarization tasks include an accuracy metric except T7, which will
only be right or wrong, and therefore cannot meaningfully be measured by
a distance.

\subsection{Conceptual Tasks}
\label{sub:conceptual_tasks}

In Table~\ref{tab:conceptual_results}, we are able to see an overview of
the results from the conceptual questions.

\begin{table*}[htpb]
  \centering
  \caption{Results from the conceptual questions}
  \label{tab:conceptual_results}
  \begin{tabular}{ll|r|lrr|rrr}
    Question                      & Commit & Answer & Median & Mean  & Variance & Median(s) & Mean(s) & Variance(s)\\\hline\hline
    Number of commits in the tree & \comA  & 1      & 4      & 19.11 & 753.11   & 10.0      & 49.92   & 5952.08\\
    Number of merges in the tree  & \comA  & 1      & 5      & 8.27  & 53.62    & 7.5       & 24.67   & 884.42\\\hline
    Number of commits in the tree & \comB  & 5      & 4      & 7.80  & 136.84   & 31.5      & 106.83  & 54123.42\\
    Number of merges in the tree  & \comB  & 3      & 3.5    & 5.40  & 50.27    & 11.0      & 65.6    & 29798.82\\
  \end{tabular}
\end{table*}

Users were able to more closely estimate the number of commits and
merges in the larger tree, but generally took longer than the smaller
tree. The tree with a single node resulted in more variability in the
estimate of number of commits.

It should be noted that these questions were answered after spending
roughly ten minutes attesting to draw a picture that held the answers to
these questions.

\subsection{Summarization Tasks}
\label{sub:summarization_tasks}

In Figure~\ref{fig:summarization_results}, we see all of the
correctness, accuracy, and timing results. The first row of plots are
the correctness results. We see in all cases except for T10, that the
number of instances of a correct result with \tool is roughly the same
as the number of incorrect instances with Gitk. We test each task with
the McNemar Chi-square test~\cite{McNemar1947}.

\begin{figure*}[htpb]
  \centering
  \includegraphics[width=\textwidth]{figures/userstudy/results.pdf}
  \caption{Results from the summarization tasks. The first row plots the
    correctness metric for each task. The second row plots the
    accuracy metric for each task. The third row plots the time metric
    for each task.}
  \label{fig:summarization_results}
\end{figure*}

With the McNemar's tests, we analyze the participants that change from
being correct with one tool to being incorrect with the other. This does
not take into account the number of people who were able to provide the
correct answer for both tools, nor the people who were incorrect for both
tools. The results show whether providing the participants with \tool
over the current standard, gitk, improves the correctness of the
summarization tasks among the participants. We show the results for the
number of people who were, with both tools, correct, incorrect, and
changed in Table~\ref{tab:correctness_table}.

In all cases, except for task T10, we saw statistically significant
results suggesting that we reject the null hypothesis. We tested each
correctness with an $\alpha = 0.005$. The $\chi^2$ test value with one
degree of freedom is $7.879$.

\begin{table*}[htpb]
  \centering
  \caption{Correctness tables showing how many people stayed correct,
    incorrect, and how many people changed between tool}
  \label{tab:correctness_table}
  \begin{tabular}{c|c|c}

    T4 & T5 & T6\\
  \begin{tabular}{cc|rr}
                           &           & \multicolumn{2}{c}{Linvis}\\
                           &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
                           & Incorrect & 15                           & 2\\
  \end{tabular} &

  \begin{tabular}{cc|rr}
                           &           & \multicolumn{2}{c}{Linvis}\\
                           &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                           & Incorrect & 14                           & 4\\
  \end{tabular}

  &

  \begin{tabular}{cc|rr}
                           &           & \multicolumn{2}{c}{Linvis}\\
                           &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                           & Incorrect & 16                           & 2\\
  \end{tabular}

  \\\hline
  T7 & T8 & T9\\

  \begin{tabular}{cc|rr}
                           &           & \multicolumn{2}{c}{Linvis}\\
                           &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}  & Correct   & 8                            & 0\\
                           & Incorrect & 13                           & 2\\
  \end{tabular}  &
  \begin{tabular}{cc|rr}
                           &           & \multicolumn{2}{c}{Linvis}\\
                           &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
                           & Incorrect & 15                           & 2\\
  \end{tabular} &
  \begin{tabular}{cc|rr}
                           &           & \multicolumn{2}{c}{Linvis}\\
                           &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
                           & Incorrect & 14                           & 3\\
  \end{tabular}\\\hline

  & T10 & \\
  & \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
    \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
                            & Incorrect & 8                            & 0\\
  \end{tabular} & \\

  \end{tabular}
\end{table*}

The correctness test statistics and conclusion for each summarization
task;

The correctness test statistics, conclusions, and a description of the
accuracy and timing results for each summarization task follow:

    T4; the resulting $\chi^2$ value is $15$. $15 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining the series of merges that a commit
    takes, with $99.5\%$ confidence.

    There is almost no variation in accuracy between participants using
    \tool, while there is more variance in Gitk. There were two outliers
    among the instances using \tool, which lie within the second and
    third quartiles for the accuracy measure of Gitk. The furthest
    outlier for \tool lies at a distance that is slightly greater than
    the median for Gitk.

    We see similar results in the timing metric; all significant data
    occurs within less time than the second, third, and fourth quartile
    of the Gitk results. Nearly all outlier instances in \tool are
    within the third quartile group of the instances of Gitk with the
    exception of the most extreme, which lies in the fourth quartile
    group.

    The results indicate that \tool is able to assist users with
    determining how a commit is merged more accurately, and more
    quickly.

    T5; the resulting $\chi^2$ value is $14$. $14 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining the other related commits, with
    $99.5\%$ confidence.

    There is very little variance in the accuracy of results for \tool
    compared to the accuracy of the results in Gitk. The median distance
    is smaller, indicating that the participants performed more
    accurately using \tool.

    There is less variance in the time taken to come to an answer with
    \tool than with Gitk. Furthermore, we see that a majority of the
    participants were able to complete the task in \tool in much less
    time than 50\% of the participants using Gitk.

    The results indicate that \tool is able to assist users in
    understanding which commits are related to a given commit.

    T6; the resulting $\chi^2$ value is $16$. $16 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining the number of authors involved with
    the merge tree, with $99.5\%$ confidence.

    We see the same results from this task as with the previous tasks,
    suggesting that \tool assists users determine the number of authors
    more quickly and more accurately.

    T7; the resulting $\chi^2$ value is $13$. $13 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining who contributed the most changes,
    with $99.5\%$ confidence.

    This question does not include an accuracy metric, as there are only
    two possible outcomes. We see the same result in the timing metric
    as we did from the previous questions.

    The results suggest that \tool is able to help users correctly
    identify the person who contributed the most lines of code to a
    merge tree in less time.

    T8; the resulting $\chi^2$ value is $15$. $15 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining how many files were contributed,
    with $99.5\%$ confidence.

    The results of this task are the same as in the previous tasks.
    This suggest that \tool is able to assist users determine how many
    files were modified, more quickly and more accurately.

    T9; the resulting $\chi^2$ value is $14$. $14 > 7.879$, therefore we
    reject the null hypothesis that \tool does not make a difference in
    the correctness when determining which file had the most changes,
    with $99.5\%$ confidence.

    While this question appears to have a similar answer to the correct
    answer for T7, the answer \comA had two files with the same number
    of midifications, thus the participant must correctly identify both
    of these files to be correct. For this reason, we include an
    accuracy metric.

    The results of this task are the same as the previous tasks.
    This suggests that \tool is able to assist users to determine which
    file had the most changes.

    T10; the resulting $\chi^2$ value is $5.44$. $5.44 < 7.879$,
    therefore we do not reject the null hypothesis, suggesting that
    \tool does not make a difference in determining which modules are
    involved with a merge tree.

    The accuracy and timing results for this task are the same as the
    others, showing that there is less variability in both accuracy and
    the time taken to have an answer between participants using \tool
    than using Gitk. Looking Table~\ref{tab:correctness_table}, we can
    see that, unlike the other questions, a majority of the participants
    were correct using both tools.

\subsection{User Opinions}
\label{sub:user_opinions}

Among the 12 pariticipants, there was nearly unanimous agreement that
for conceptual understanding and summarization tasks, \tool was easier
to work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git commandline may be to
extract the a good conceptual understanding from the DAG, and perform
the summarization tasks from the commandline. One of these three
participants said that they would prefer to have both tools available,
as they are able to complement eachother.
